Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-13 SDSS-2023/testing-charts-accuracy.qmd
link to data folder

library(readxl)
library(lubridate)
library(patchwork)
library(survey)
#library(ggmosaic)
library(ggpcp)
library(broom)
library(latex2exp)
library(gt) # grammar of tables

@@

vs_repo_local <- "~/Documents/projects/NORC" # link to local version of the visual_studies repo
```

```{r data}
# other github repo. 
round1 <- readRDS("~/Documents/projects/NORC/visual-studies/data/round1.rds")
round2 <- readRDS("~/Documents/projects/NORC/visual-studies/data/round2.rds")

>>>>

library(readxl)
library(lubridate)
library(patchwork)
library(survey)
#library(ggmosaic)
library(ggpcp)
library(broom)
library(latex2exp)
library(gt) # grammar of tables
library(here)

@@

vs_repo_local <- here::here("data") # link to data folder
```

```{r data}
# other github repo. 
round1 <- readRDS(file.path(vs_repo_local, "round1.rds"))
round2 <- readRDS(file.path(vs_repo_local, "round2.rds"))
